Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-21 paper.tex
fix typos in fig11
a little progress

This section presents our second contribution, a framework for proving
correctness of cast representations. The next section will apply this
framework to prove the correctness of the \lazyD{} hypercoercions.

We start by defining a CEK machine \effCEK{C} that is parameterized
over the cast representation $C$. This machine is space efficient
provided that the cast representation performs compression.  The
interface between the machine and the cast representation is defined
by an abstract data type, named Cast ADT, that we define shortly.
%

\todo[inline]{UNDER CONSTRUCTION. -JS}

If $C$, an implementation of the Cast ADT inteface, satisifies a collection of 
properties that we defined as Lazy D Cast ADT. We can instantiate our framework 
theorem that we define shortly to prove that evaluating an program in 
\effCEK{C} gives the same result as \ineffCEKD. We are working on a
similar theorem for \lazyUD{}.

\todo[inline]{UNDER CONSTRUCTION. -KC}

The framework is a theorem saying that for all cast representation $C
$, if $C$ satisfies a collection of properties, then it would
respect the Lazy D semantics of cast calculi. We are working on a
similar theorem for \lazyUD{}.

%then instantiating our parameterized space-efficient interpreter with$C$
%gives an interpter that is extensionally equal to the standard interpreter for 
%\lazyD\ cast calculus.

>>>>

This section presents our second contribution, a framework for proving
correctness of cast representations, especially space efficient
ones. Section~\ref{sec:hypercoercion-correctness} will apply this
framework to prove the correctness of the \lazyD{} hypercoercions.

We start by defining a CEK machine \effCEK{C} that is parameterized
over the cast representation $C$. This machine is space efficient
provided that the cast representation performs compression.  The
interface between the machine and the cast representation is defined
by an abstract data type, named Cast ADT, that we define shortly.

When then prove that, for any instance $C$ of the Cast ADT, \effCEK{C}
is equivelent to \ineffCEKD{] provided that $C$ satisfies a collection
of properties that we call the Lazy D Cast abstract data type.
In Section~\ref{sec:hypercoercion-correctness} we show that
the \lazyD{} hypercoercions $H$ are an instance of the Lazy D ADT,
and therefore \effCEK{H} is equivalent to \ineffCEKD{}.

We are working on a similar theorem for \lazyUD{}.

\todo[inline]{UNDER CONSTRUCTION -JS}
